---
title: "linear model from Web"
author: "Sophia Castellon"
date: "October 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
plot(SIMS~ARM, data=data)
model.1=lm(SIMS~ARM, data=data)
abline(model.1)
```

This scatter plot shows a positive relationship between simulation score and arm strength. Simulation strength increases as arm strength increases. 

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
With a correlation of 0.69 there is moderate positive correlation between the SIMS score and ARM strength.

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

model.1 shows that the intercept -4.095 and coefficient 0.055 of ARM are both of these are significantly different from zero.

#### Predict at target point

```{r}
targtPoint = data.frame(GRIP=94, ARM=88)
perdictInt= predict(model.1, targtPoint, interval = 'prediction')
print (perdictInt)
```


#### scatterplot with model fit
  
At AMR=88, GRIP=94 the predicted SIMS score is 0.71. At that score the 95% confidence interval for that score ia SIMS between -1.73 and 3.14

## Model 2 SIM~GRIP

```{r}
plot(SIMS~GRIP,data=data)
model.2=lm(SIMS~GRIP, data=data)
abline(model.2)
```

### Now add in scatterplot

The scatter plot shows that simulated strength score increases depending on the amount of the GRIP strength exerted by an individual. 

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```
The numerical results show that the correlation equals 0.64 shows that there is a moderate positive correlation between simulated strength scores and ARM strength 

### Inferential results 

```{r}
model.2 <- lm(SIMS~GRIP, data=data)
summary.lm(model.2)
```
the model shows that the intercept -4.809 and coefficient 0.045 GRIP are bpth significantly different from zero. 
  
#### predict model.2 at target point

```{r}
targtPoint = data.frame(GRIP=94, ARM=88)
predictInt= predict(model.2, targtPoint, interval = 'prediction')
print(predictInt)
```
At ARM=88, GRIP=94, the predicted SIMS score is -0.54. At that score the 95% confident interval shows that the score of SIMS is between -3.11 and 2.04

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

```{r}
model.3 = lm(SIMS~ARM+GRIP,data=data)
summary(model.3)
```
Model.3 shows that intercept -5.434, coefficient 0.038 of ARM, and coefficient of GRIP is 0.025 and they are all significantly different from zero 

### Numerical results (cor)

```{r}
cor(data)
```
Sims correlates with GRIP and ARM with these values 
  

#### predict model.3 at target point
  
```{r}
predict(model.3,targtPoint,interval='prediction')
```
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

```{r}
anova_results <-anova(model.1,model.3)
print(anova_results)
```

The P value of the comparison of model.2 and model.3 is 0.000000001495 which is less than 0.05. this means that the models are different and model.3 is better
